\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeCompany}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://whereistejas.github.io}{\Large Tejas Sanap}} & Email : \href{mailto:sanap.tejas@gmail.com}{sanap.tejas@gmail.com}\\
  \href{https://whereistejas.github.io}{https://whereistejas.github.io} & Mobile : +91 - 9765 698 365 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
	\resumeSubHeadingListStart
	  \resumeSubheading
		{Sinhagad Academy of Engineering}{Pune, India}
		{Bachelor of Engineering in Mechanical Engineering;  GPA: 7.75/10.0}{Aug. 2016 -- Jul. 2019}
	  \resumeSubheading
		{K. K. Wagh Institue}{Nashik, India}
		{Diploma in Mechanical Engineering; Percentage: 79\%}{2013 -- 2016}
	  \resumeSubheading
	    {Podar International School}{Nashik, India}
		{ICSE; Percentage: 89\%}{2008 -- 2013}
	\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
	\resumeCompany
      {Wipro Ltd.}{Pune, India}
      {Project Engineer}{Oct. 2019 - Present}
		\resumeSubHeadingListStart
		\resumeSubheading
		  {Client: Johnson and Johnson}{}
		  {ABAP and HANA Developer}{Feb 2020 - Present}
			\resumeItemListStart
				\resumeItem{oData Services}
				  {Regular enhancements and patches to pre-existing oData V2 services for Access Control request creation, approval and status and mitigation control application in SAP GRC.}
				\resumeItem{GRC Database Migration}
				  {GRC Platform migrated from Oracle database to HANA databse.}
				\resumeItem{GRC 10.1 to GRC 12.0 Upgrade}
				  {Participated in one complete E2E implementation, hypercare and support cycle during major version upgrade.}
				\resumeItem{User Transfer Application}
				  {This application transfers the ownership of all the master data objects from one user to another. Complete backend development including business logic using Object Oriented ABAP, Unit testing for business logic and oData services.}
				\resumeItem{User to Role Report and Mitigation Control Report} 
				  {Converted slow ABAP reports that processed large volumes of data to Stored Procedures and Calculaton Views in HANA, to increase report execution speed. Also, created the front-end UI using Fiori Elements.}
				\resumeItem{Miscelleneous}
				  {
					\begin{itemize}
						\item Wrote python scripts to translate i18n files from English to 22 other languages.
						\item Wrote python scripts for manipulating large datasets using pandas and numpy.
					\end{itemize}
				  }
			\resumeItemListEnd
		\resumeSubHeadingListEnd
	\resumeCompany
		{Magna Automotive}{Pune, India}
		{Intern in Industrial Engineering}{Oct. 2018 -- Mar. 2019}
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------PROJECTS-----------------
\section{Awards}
  \resumeSubHeadingListStart
	  	\resumeSubheading
	  	  {Best Campus to Corporate New Joinee}{}
		  {Wipro Compliance and Risk Services Business Unit}{Oct 2020}
		  \resumeItemListStart
			  \resumeItem{}{One of Top 25 performing new joinees}
		  \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------TALKS AND WORKSHOPS----------
\section{Talks and Workshops}
	\resumeSubHeadingListStart
	  	\resumeSubheading
		{\href{https://github.com/whereistejas/latex-workshop}{Workshop on LaTeX: Article, Reports and Slides}}{Nashik, India}
		  {K. K. Wagh Institute of Engineering}{Dec. 2019}
	  	\resumeSubheading
		{\href{https://github.com/whereistejas/plug-containers-talk}{Talk on Container Internals: cgroups and podman}}{Pune, India}
		  {Kernel Meetup}{Dec. 2019}
	  	\resumeSubheading
		{\href{https://github.com/whereistejas/plug-command-line}{Talk on Unix Command Line Utilties}}{Pune, India}
		  {Pune Linux Users Group}{Jul. 2019}
	\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
	\resumeSubHeadingListStart
		\item{\textbf{Languages}{: ABAP, Python, SQL, SQLScript, Bash Scripting, LaTeX} }
			\hfill
		\item{\textbf{Markup Languages}{: HTML and CSS, Markdown} }
			\hfill
		\item{\textbf{Technologies}{: SAP GRC, Unix (RHEL and Debian), AWS, Docker, Git} }
			\hfill
	\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
